---
title: "TidyTemplate"
date: 2021-01-04
output: html_output
---

# TidyTuesday

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(RColorBrewer)
library(ggflags)
library(gapminder)
library(countrycode)
library(ggthemes)
library(here)
```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2021-01-05")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

transit_cost <- tt$transit_cost


```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}

str(transit_cost)

continents = countrycode::codelist %>%
  select(ecb, country.name.en, continent) %>%
  rename(country = country.name.en)

transit_cost_tidy <- transit_cost %>%
        rename(ecb = country) %>%
        mutate(ecb = if_else(ecb == "UK", "GB", ecb)) %>%
        left_join(continents, by = "ecb") %>%
        mutate(
        start_year = as.double(start_year),
        end_year = as.double(end_year),
        real_cost = as.double(real_cost),
        tunnel_per = (parse_number(tunnel_per)/100),
        ecb = tolower(ecb)) #need lower case to match country flag icons #recode uk to gb for flag #learned from jsakaluk
       
        
        
        
        #mutate(country_fullname = countrycode(sourcevar = transit_cost_tidy$country, origin = "iso2c", destination = "country.name"))

str(transit_cost_tidy)        
#unique(transit_cost_tidy$city)

city_cost_tidy <- transit_cost_tidy %>%
        group_by(city, continent, ecb) %>%
        summarise(avg_cost_km = mean(cost_km_millions)) %>%
        ungroup() %>%
        arrange(-avg_cost_km) %>%
        head(15)

#Calculate expensive and cheap cities
#calculate more efficient construction times

```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}

plot <- city_cost_tidy %>%
ggplot(aes(x = reorder(city, avg_cost_km), y = avg_cost_km, fill = continent)) +
        geom_col(alpha = 0.8) +
        geom_flag(y = -50, aes(country = ecb, size = 1)) +
        expand_limits(y = 0)+
        coord_flip()+
        theme_economist(horizontal = FALSE)+
        theme(legend.position = c(.7,.8),
              axis.text.x = element_text(vjust = 3)) +
        guides(color = TRUE, size = FALSE) +
        labs(fill = "",
             title = "New York, New York",
             subtitle = "Top 15 expensive cities for transit infrastructure") +
        xlab("") + 
        ylab("Average cost/km in millions of USD by city") +
        scale_fill_manual(values = c("Oceania" = "#4D9DE0", 
                                "Americas" = "#E15554", 
                                "Africa" = "#E1BC29", 
                                "Asia" = "#3BB273", 
                                "Europe" = "#7768AE"))


#mean(city_cost_tidy$avg_cost_km)
#mean(transit_cost_tidy$cost_km_millions,na.rm = TRUE)  
```

# Save Image

```{r}

# This will save your most recent plot
ggsave(plot,
       filename = here::here("Output","2020_01_05_transit_cost","transit_cost.png"),
       dpi= 300,
       height = 6,
       width = 8)

#create  folder first

```
